On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-16 main.tex
final proof

\begin{theorem}\label{thm:greedy-bisim-one-dead}
    Consider two states in GKAT coalgebras \(s ∈ S, u ∈ U\) and an arbitrary bisimulation \(≈\), if \(s\) is dead, then 
    \begin{itemize}
        \item if \(u\) is not dead, then \((s, u) ∉ {≈}\).
        \item if \(u\) is dead, 
    \end{itemize}
\end{theorem}

>>>>

\begin{theorem}\label{thm:greedy-bisim-one-dead}
    Consider two states in GKAT coalgebras \(s ∈ S, u ∈ U\) and an arbitrary bisimulation \({∼} ⊆ \norm(S) × \norm(U)\), if \(s\) is dead, then 
    \begin{enumerate}
        \item\label{itm:greedy-bisim-one-dead-then-both-dead} if \(s ∼ u\), then \(u\) is dead.
        \item\label{itm:remove-dead-pairs-sound} if \(u\) is dead, then \({∼} ∖ ⟨(s, u)⟩_∼\) is also a bisimulation between \(\norm(S)\) and \(\norm(U)\).
    \end{enumerate}
\end{theorem}

\begin{proof}
    \Cref{itm:greedy-bisim-one-dead-then-both-dead} is a consequence of bisimulation preserves liveness (\Cref{thm:bisim-preserve-liveness}) and normalization preserves liveness (\Cref{thm:norm-perserve-liveness}).

    \Cref{itm:remove-dead-pairs-sound} can be proven by realizing that \((s, u)\) is a dead state in \(∼\) (\Cref{thm:bisim-preserve-liveness}) which means that all the states in \(⟨(s, u)⟩_∼\) are dead.
    Because \(∼\) is a normalized GKAT coalgebra (\Cref{thm:}), therefore no state can transition into dead states like \(⟨(s, u)⟩_∼\), hence \({∼} ∖ ⟨(s, u)⟩_∼\) is still closed under its transition, and form a GKAT coalgebra.
    And the fact that \({∼} ∖ ⟨(s, u)⟩_∼\) is also a bisimulation can be proven by factoring through \(∼\) via the inclusion homomorphism:
    \begin{align*}
        ({∼} ∖ ⟨(s, u)⟩_∼) \xrightarrow{i} {∼} \xrightarrow{π₁} \norm(S) \\
        ({∼} ∖ ⟨(s, u)⟩_∼) \xrightarrow{i} {∼} \xrightarrow{π₂} \norm(U)
    \end{align*}
    TODO: extract the above to a lemma.
\end{proof}
